\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{lmodern}

% Estilo Classic: nombre a la izquierda, datos a la derecha
\moderncvstyle{classic} 
\moderncvcolor{blue} 

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{bookmark}

% Márgenes optimizados para una sola página
\geometry{left=1.5cm, top=1.2cm, right=1.5cm, bottom=1.2cm}

% --- INFORMACIÓN PERSONAL ---
\firstname{Ignacio}
\familyname{Valmaseda}
\title{Quantitative Analytics Specialist}
\address{San Borondón 107}{35500, San Bartolomé, Las Palmas}{Spain}
\mobile{(+34) 664-645-676}
\email{ignacio.0032@gmail.com}
\social[linkedin]{ignaciovalmaseda}

%----------------------------------------------------------------------------------
%            CONTENIDO
%----------------------------------------------------------------------------------

\begin{document}
\makecvtitle

\section{Professional Summary}
\cvitem{}{Senior Quantitative Analyst and Physicist with 7+ years of experience transforming complex data into strategic financial assets. Specialist in \textbf{end-to-end development of analytical tools} (R/Shiny) and advanced modeling (Capital, Risk, Profitability). Entrepreneurial mindset focused on process automation and scalable modeling.}

\section{Experience}

\cventry{2025--Present}{Risk \& Analytics Specialist}{Santander Analytics}{Madrid / Remote}{}{
Leading technical methodology and capital optimization at a global scale.
\begin{itemize}
    \item \textbf{Capital Modeling:} Architect and maintain core models for Asset Correlation, Capital Consumption, and DTAs, optimizing the bank's capital structure.
    \item \textbf{Profitability Engineering:} Defined and automated the calculation of \textbf{RORAC} and \textbf{RORWA} metrics, directly impacting strategic decision-making.
    \item \textbf{Pension Risk Leadership:} Lead methodological modeling for Pension Risk, ensuring compliance and mathematical rigor under international standards.
    \item \textbf{Consultancy \& Support:} Act as an internal consultant providing model replicas, independent validation, and methodological support for complex financial operations.
\end{itemize}}

\cventry{2018--2025}{Quantitative Risk Analyst}{Santander Analytics}{Madrid}{}{
Developed data-driven solutions for risk management and financial visualization.
\begin{itemize}
    \item \textbf{Product Development:} Built and deployed advanced \textbf{R/Shiny applications} to visualize and manage complex exposures, reducing reporting time and increasing data transparency.
    \item \textbf{Regulatory Modeling:} Designed risk models (Counterparty \& Capital) aligned with CRR/Basel III, bridging the gap between technical math and business requirements.
    \item \textbf{Advanced Analytics:} Specialized in financial projections and extrapolations using physics-based statistical approaches to forecast portfolio behavior.
\end{itemize}}

\cventry{2018}{Quantitative Trainee}{Santander Analytics}{Madrid}{}{
\begin{itemize}
    \item Improved feature engineering for mathematical models and automated technical documentation processes.
\end{itemize}}

\section{Technical Stack \& Expertise}
\cvitem{Programming}{\textbf{R \& SHINY (Expert)}, SQL (Advanced), Excel/VBA (Expert), \LaTeX, Git, Python \& C++ (Intermediate).}
\cvitem{Quantitative}{Financial Modeling, \textbf{Capital Theory}, Pension Risk, Bayesian Statistics, Asset Correlation, RWA Optimization.}
\cvitem{Business}{Wholesale Banking, Profitability Analysis (RORAC), Corporate Valuation, Collateral Management.}
\cvitem{Languages}{Spanish (Native), \textbf{English (C1 Advanced - BEC Higher)}.}

\section{Education}
\cventry{2017--2018}{MSc. Finance and Banking}{Garrigues Study Center}{Madrid}{}{Specialized in Markets and European Regulations.}
\cventry{2016--2017}{MSc. Biostatistics}{Complutense University of Madrid}{Madrid}{}{Focus on Probability, Mixed Models, and Simulation.}
\cventry{2010--2016}{BSc. Physics}{Complutense University of Madrid}{Madrid}{}{Specialization in Meteorology and Complex Systems.}

\end{document}