\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{lmodern}

% Estilo de la plantilla
\moderncvstyle{classic} 
\moderncvcolor{blue} 

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}

% Ajuste de márgenes
\geometry{left=1.5cm, top=1.5cm, right=1.5cm, bottom=1.5cm}

% --- INFORMACIÓN PERSONAL ---
\firstname{Ignacio}
\familyname{Valmaseda}
\title{Analytics Specialist}
\address{San Borondón 107}{35500, San Bartolomé}{Spain}
\mobile{(+34) 664-645-676}
\email{ignacio.0032@gmail.com}
\social[linkedin]{ignaciovalmaseda}

%----------------------------------------------------------------------------------
%            CONTENIDO
%----------------------------------------------------------------------------------

\begin{document}
\makecvtitle

\section{Professional Summary}
\cvitem{}{Risk Specialist with extensive experience in Wholesale Banking and Risk Methodology. Expert in profitability metrics (RORAC, RORWA) and Capital Modeling (RWA, DTAs). Strong background in Physics and Biostatistics, specializing in developing complex analytical tools and model replicas to drive strategic decision-making.}

\section{Work Experience}

% NUEVO PUESTO: RISK SPECIALIST
\cventry{2025--Present}{Risk Specialist}{Santander Analytics, Santander Bank}{Madrid}{Full-time}{
Leading technical initiatives in Wholesale Banking and Risk Methodology, focusing on capital optimization and profitability metrics.
\begin{itemize}
    \item Define and support the calculation of key profitability metrics, including \textbf{RORAC} and \textbf{RORWA}, for strategic decision-making.
    \item Model and update core Capital Models: Asset Correlation, Capital Consumption, Deferred Tax Assets (DTAs), Goodwill, and Diversification effects.
    \item Lead the methodology and modeling for \textbf{Pension Risk}, ensuring alignment with actuarial and regulatory standards.
    \item Provide end-to-end methodological support, including model replicas, independent testing, and validation of complex financial calculations.
    \item Manage comprehensive monitoring and reporting frameworks for internal control and regulatory validation processes.
\end{itemize}}

% PUESTO ANTERIOR: RISK ANALYST
\cventry{2018--2025}{Risk Analyst}{Santander Analytics, Santander Bank}{Madrid}{Full-time}{
Focused on data modeling, profitability operations, and risk management visualization.
\begin{itemize}
    \item Created models to measure profitability and manage counterparty and capital risks according to CRR/Basel III standards.
    \item Developed advanced R/Shiny applications to facilitate the visualization of complex financial datasets and risk exposures.
    \item Performed advanced data analysis for financial projections, risk extrapolations, and valuation results.
    \item Conveyed technical financial concepts to business areas and resolved methodological doubts regarding risk operations.
\end{itemize}}

% BECA
\cventry{Jun--Oct 2018}{Risk Trainee}{Santander Analytics, Santander Bank}{Madrid}{Full-time}{
Initial experience in risk methodology and data representation within the banking sector.
\begin{itemize}
    \item Assisted in the analysis of complex datasets and supported the improvement of existing mathematical models.
    \item Developed features for data representation and drafting of technical model documentation for internal audits.
    \item Learned to translate technical risk concepts into business-oriented insights.
\end{itemize}}

\section{Skills}
\cvitem{Finance}{Profitability Analysis (RORAC, RORWA), Capital Modeling (Asset Correlation, RWA, DTAs), Pension Risk, Wholesale Banking Operations, Corporate Valuation.}
\cvitem{Software}{R \& SHINY (Expert), Excel \& VBA (High), LaTeX (Medium), SQL (Medium).}
\cvitem{Languages}{Spanish (Mother tongue), English (Fluent: C1 Advanced, BEC Higher).}

\section{Education}
\cventry{2017--2018}{MSc. Master's Degree in Finance and Banking}{Garrigues Study Center}{}{}{Financial markets, corporate banking, and european regulations.}
\cventry{2016--2017}{MSc. Master's Degree in Biostatistics}{Complutense University of Madrid}{}{}{Probability, mixed models and bayesian statistics.}
\cventry{2010--2016}{BSc. Degree in Physics}{Complutense University of Madrid}{}{}{Meteorology and atmospheric physics specialization.}

\end{document}