\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{lmodern}

\moderncvstyle{classic} 
\moderncvcolor{blue} 

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{bookmark}

\geometry{left=1.5cm, top=1.2cm, right=1.5cm, bottom=1.2cm}

% --- INFORMACIÓN PERSONAL ---
\firstname{Ignacio}
\familyname{Valmaseda}
\title{Quantitative Finance Specialist | Profitability Architect}
\address{}{San Bartolomé, Las Palmas}{Spain}
\mobile{(+34) 664-645-676}
\email{ignacio.0032@gmail.com}
\social[linkedin]{ignaciovalmaseda}

\begin{document}
\makecvtitle

\section{Professional Summary}
\cvitem{}{Physicist and Quant with a "heavy-duty" approach to banking profitability. 7+ years architecting complex financial engines for Wholesale Banking. Expert in \textbf{stress-testing profitability} (RORAC/RORWA) and simulating capital consumption under extreme regulatory constraints. I don't just report numbers; I build the models that define how capital is deployed and how massive operations are structured.}

\section{The "Hard" Expertise}
\cvitem{Profitability}{Industrial-scale \textbf{RORAC/RORWA} modeling, deal structuring (Assets \& Liabilities), and P\&L optimization.}
\cvitem{Simulation}{Advanced Monte Carlo simulations, Asset Correlation modeling, and \textbf{Capital Consumption (RWA)} stress testing.}
\cvitem{Quant Stack}{Expert \textbf{R/Shiny development} (financial apps), SQL, and complex Excel/VBA engineering. Physicist-level math applied to Pension Risk and DTAs.}
\cvitem{Mechanics}{Collateral optimization, complex amortization math, and regulatory engineering (CRR/Basel III).}

\section{Experience}

\cventry{2025--Present}{Quantitative Risk Specialist}{Santander Analytics}{Madrid / Remote}{}{
Responsible for the methodological core and profitability simulation engine for Wholesale Banking.
\begin{itemize}
    \item \textbf{Profitability Engineering:} Architected and maintain the calculation logic for \textbf{RORAC and RORWA}, optimizing how the bank imputes capital to large-scale operations.
    \item \textbf{Capital Dynamics:} Model and simulate core capital components (Asset Correlation, DTAs, Goodwill) to forecast and minimize capital consumption.
    \item \textbf{Deal Structuring Support:} Provide technical "firepower" for complex banking deals, simulating the impact of \textbf{financial \& mortgage guarantees} on the overall RWA.
    \item \textbf{Pension Risk Modeling:} Developed the quantitative framework for pension risk valuation and actuarial-financial alignment.
    \item \textbf{Technical Validation:} Perform high-precision model replicas and independent testing to ensure the integrity of regulatory capital engines.
\end{itemize}}

\cventry{2018--2025}{Quantitative Analyst}{Santander Analytics}{Madrid}{}{
\begin{itemize}
    \item \textbf{Financial Tooling:} Engineered advanced R/Shiny platforms to visualize and simulate real-time profitability across diverse banking portfolios.
    \item \textbf{Operational Math:} Built specialized models for complex amortization schedules and funding cost (FTP) integration.
    \item \textbf{Regulatory Stress Testing:} Simulated the impact of evolving CRR/Basel frameworks on the bank's operational profitability and risk exposure.
\end{itemize}}

\cventry{2018}{Risk Trainee}{Santander Analytics}{Madrid}{}{
\begin{itemize}
    \item Assisted in initial counterparty risk modeling and technical documentation for mathematical audits.
\end{itemize}}

\section{Education}
\cventry{2017--2018}{MSc. Finance and Banking}{Garrigues Study Center}{Madrid}{}{Quantitative focus on Markets and Regulation.}
\cventry{2016--2017}{MSc. Biostatistics}{Complutense University of Madrid}{Madrid}{}{Heavy focus on Probability and Bayesian Simulation.}
\cventry{2010--2016}{BSc. Physics}{Complutense University of Madrid}{Madrid}{}{Theoretical Physics, Meteorology, and Complex Systems.}

\end{document}